Ceph Parallel File System Evaluation Report

### 2013-08-20 ceph-eval.tex
Add XFS justification and Brtfs footnote

Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
Due to its performance and maturity, we chose XFS. We experimented with XFS to
acquire a set of configuration parameters which provided optimal performance for
the SFA10K. We sampled a selected set of parameters (block size, queue depth,
request size, sequential read and write). We settled on the following
configuration: mount with \verb!nobarrier,noatim,inode64! options.
The \verb!inode64! option had a notable improvement on sequential write (around
20\%).

>>>>

Ceph supports multiple backend file systems including Btrfs, Ext4, and XFS.
Due to its maturity and Inktank's recommendations, we chose XFS.\footnote{It
should be noted that in testing cases while we can compare XFS vs.
Brtfs, Brtfs generally shows better performance results.} We experimented with
XFS to acquire a set of configuration parameters which provided optimal
performance for the SFA10K. We sampled a selected set of parameters (block size,
queue depth, request size, sequential read and write). We settled on the
following configuration: mount with \verb!nobarrier,noatim,inode64! options.
The \verb!inode64! option had a notable improvement on sequential write (around
20\%).
